Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-20 paper/paper.tex
Change introduction section - first paragraph

In the past decade, technology has drastically increased its influence on 
virtually every aspect of our society. Therefore, software projects have 
inherently become more complex and require increasing number of developers in
the team. Due to this, software engineers have created issue tracking systems,
a means of planning, managing and tracking work products in the form of 
\emph{software tickets} or \emph{issues}.

@@

Even though tickets provide such comprehensive data regarding a specific task, studies have shown 
that fixing bugs is one of the most common tasks performed by developers \cite{latoza2006maintaining}. One of
the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
decreased customer satisfaction and overall poor performance.

>>>>

In the past decade software projects have inherently become more complex and require increasing number of developers in
the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
transitioned from small, collocated to globally distributed teams. One reason elicited in the paper is the increasing 
popularity of communication tools, such as Slack or Google Hangouts. Due to this, developers have created issue tracking 
systems as means of planning, managing and tracking work products in the form of \emph{software tickets} or \emph{issues}.

@@

Even though tickets provide such comprehensive data regarding a specific task, studies have shown 
that fixing bugs is one of the most common and time consuming tasks performed by developers \cite{latoza2006maintaining}. One of
the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
decreased customer satisfaction and overall poor performance.
